Incremental λ-Calculus in Cache-Transfer Style

### 2017-07-17 popl18/soundness.tex
Revise theorem text

\begin{theorem}[Soundness of CTS differentiation wrt differentiation]
  \label{thm:soundness-compiled-changesfinal}
  Let $\tcache$ and $\tterm$ be such that 
  $(\tcache, \tterm) = \compileterm{\bullet}{\sterm}$.
  For all $\iectx, \sterm$ and $\icloseddvalue$,
  $\seval{\iectx}{\iderive\sterm}{}{\icloseddvalue}$,
  for $\old\tdectx$ and $\new\tdectx$ such that
  $\oldenvwithcache{\compile\iectx}{\tcache}{\old\tdectx}$
  and $\newenvwithcache{\compile\iectx}{\tcache}{\new\tdectx}$,
  $\seval{\oldenv{\old\tdectx}}{\tterm}{}{(\old\tclosedvalue, \oldtcachedclosedvalues)}$ and
  $\seval{\newenv{\new\tdectx}}{\tterm}{}{(\new\tclosedvalue, \newtcachedclosedvalues)}$,
  then
  $
  \seval{\old\tdectx}{\derive\tcache\sterm}{}{(\compile{\icloseddvalue}, \newtcachedclosedvalues)}
  $.
\end{theorem}

>>>>

\begin{theorem}[Soundness of CTS differentiation wrt differentiation]
  \label{thm:soundness-compiled-changesfinal}
  Let $\tcache$ and $\tterm$ be such that 
  $(\tcache, \tterm) = \compileterm{\bullet}{\sterm}$.
  For all $\iectx, \sterm$ and $\icloseddvalue$ such that
  $\seval{\iectx}{\iderive\sterm}{}{\icloseddvalue}$,
  for all $\old\tdectx$ and $\new\tdectx$ such that
  $\oldenvwithcache{\compile\iectx}{\tcache}{\old\tdectx}$,
  $\newenvwithcache{\compile\iectx}{\tcache}{\new\tdectx}$,
  $\seval{\oldenv{\old\tdectx}}{\tterm}{}{(\old\tclosedvalue, \oldtcachedclosedvalues)}$ and
  $\seval{\newenv{\new\tdectx}}{\tterm}{}{(\new\tclosedvalue, \newtcachedclosedvalues)}$,
  we have
  $
  \seval{\old\tdectx}{\derive\tcache\sterm}{}{(\compile{\icloseddvalue}, \newtcachedclosedvalues)}
  $.
\end{theorem}
